\documentclass[a4paper,12pt]{article}
\usepackage{hyperref}

\title{Software Engineering Group Project \\ Activities Report\\Milestone 4}
\author{Mohammad Bamogaddam}
\date{17 August 2008}


\begin{document}

\maketitle

\section*{Objective}
This report records my activities related to Earth project development for Milestone 4 period from 28-July-2008 to 17-August-2008.
\section*{Assigned Tasks}
\begin{enumerate}
    \item Resolve Ticket 154
    \item Improve the metadata solution from the previous milestone 
\end{enumerate}
\section*{Resources}
It was budgeted 30 hours per week. A total of 90 hours for the whole sprint

\newpage

\section*{Activities}
On this section, I am going to list all the activities during this sprint.

\begin{table}
\begin{tabular}{| l | l | c |}
\hline
Activity & Date & Spent Time (Hours) \\
\hline
Plan for milestone 4 & 30-July & 1.5 \\
\hline
Create a plan template & 30-July & 1.5 \\
\hline
Revise the current solution for files metadata & 01-August & 2 \\
\hline
Post a response on Earth Trac about ticket 42 & 02-August & 0.5 \\
\hline
Reading about rails & 02-August & 2 \\
\hline
Design the new solution for files metadata & 03-August & 1 \\
\hline
planning & 04-August & 0.5 \\
\hline
files metadata: coding  & 04-August & 1 \\
\hline
files metadata: testing & 04-August & 1 \\
\hline
Rails reading & 04-August & 1.5 \\
\hline
Ticket 154: investigation & 05-August & 1.5 \\
\hline
Ticket 154: coding and testing & 06-August & 1 \\
\hline
Files metadata: coding & 06-August & 1 \\
\hline
Rails reading & 06-August & 1 \\
\hline
unit testing problem & 06-August & 4 \\
\hline
Rails reading & 07-August & 5 \\
\hline
Rails reading & 08-August & 5 \\
\hline
planning & 09-August & 1 \\
\hline
Files metadata:coding & 09-August & 5 \\
\hline
Files metadata:coding & 10-August & 5 \\
\hline
Reading & 11-August & 1 \\
\hline
Meeting & 11-August & 1 \\
\hline
Unit testing problem & 12-August & 2 \\
\hline
Rails reading & 13-August & 5 \\
\hline
Ticket 154: more testing & 14-August & 1 \\
\hline
prepare demonstration & 15-August & 2 \\
\hline
Integration & 15-August & 2 \\
\hline
Writing report & 17-August & 2 \\
\hline
 & Total & 58 \\
\hline
\end{tabular}

\end{table}

\newpage

\section*{Progress Summary}
\begin{itemize}
   \item Ticket 154 has been implemented and tested. It is now just waiting for RSP approval. check these commits for its implementation: \\ 
\href{http://github.com/mfb1982/earth/commit/512ecee65b37234}{http://github.com/mfb1982/earth/commit/512ecee65b37234} \\
\href{http://github.com/mfb1982/earth/commit/d2fddc5b66b9530e}{http://github.com/mfb1982/earth/commit/512ecee65b37234} \\
	\item Files metadata: It is implemented and tested but it will be reimplemented again depending on the feed back from earth developers. But there was some necessary code modification which has been committed to the repository. All other modification kept on my personal repository.
Check theses commits:\\
\href{http://github.com/mfb1982/earth/commit/036b70fa2a622}{http://github.com/mfb1982/earth/commit/036b70fa2a622}\\
\href{http://github.com/mfb1982/earth/commit/ae12f79123a}{http://github.com/mfb1982/earth/commit/ae12f79123a}\\
\href{http://github.com/mfb1982/earth/commit/13a062b03b7}{http://github.com/mfb1982/earth/commit/13a062b03b7}\\
\href{http://github.com/mfb1982/earth/commit/cf80bf842}{http://github.com/mfb1982/earth/commit/cf80bf842}\\

\end{itemize}
\section*{Sprint Notes}
\begin{itemize}
	\item Contacting earth developers was very beneficial. Unfortunately, a lot of work has been done in the wrong direction but it was good to improve my rails skills.
	\item I faced a big problem with unit testing. This problem caused me a lot of trouble and waste a lot of time. Still, I could not find a solution for it.
	\item the main reason for been under the budgeted resources is because I have two other subjects. Both subjects needs a lot of work too. 
\end{itemize}
\end{document}  
