\documentclass[10pt, a4]{article}
\usepackage{times}

\begin{document}

\title{Software Engineering Group Project - 7096A}
\author{Semester 1 Week 10 Meeting - Sub-Group 1}
\date{Wed May 21, 2008 (1400hr)}

\maketitle 

\noindent {\large \textbf{\underline{Integration Testing of Milestone 1 Solutions}}}\\
\noindent {\normalsize \textbf{Assignee:} George Sainsbury}\\
\noindent {\normalsize \textbf{Hours:} 18hrs (approx)}\\
\begin{enumerate}
\item {Task Description}
  \begin{itemize}
  \item Integrate the Milestone 1 codes and verify correctness of solutions using the available testing framework.
  \end{itemize}
\item {Status}
  \begin{itemize}
  \item In the time from the last meeting (7th May) to this meeting (21st May) I have been concentrating on the integration and testing of Milestone 1. Alex and I went through each of the 5 tickets in Milestone 1 (after excluding ticket 27 which was moved to Milestone 2.) and these tickets were 66, 75, 120, 127 and 145. After inspection and discussion we noted that only tickets 75 and 145 were co-dependant in terms of functionality and that these changes could be integrated without introducing problems.
  \item I have also, as with the rest of the group, been learning about the git structure we have adopted and conventions we have chosen or developed. This is especially relevant for me because of the topic for my Honours project. Testing was also discussed in terms of the 5 tickets for Milestone 1. Tickets 75, 120, 145 are purely display changes and must be manually tested. Ticket 127 concerned itself with SVG capability and must also be manually tested on as many environments as we have access to. Ticket 66 is more complicated but the unit tests have passed and no additional tests are necessary.
  \end{itemize}
\end{enumerate}

\[\emph{End}\]

\end{document}