\documentclass{letter}

\begin{document}

{\large \textbf{\underline{Meeting Minutes Taken on 7 May, 2008 at 1415 hours}}}\\

\textbf{Attendees:} Filimoni Lutunaika, Xiaodong Cui, Alex Egan, Li Jiang\\
\textbf{Apologies:} George Sainsbury\\
\textbf{Next Meeting:} 21/05/2008 (Wednesday) @ 1400 hours\\
\textbf{Contents:}

\begin{enumerate}
\item Progress Reports
	\begin{itemize}
	\item Fil presented his report. He was investigating the continuous testing of the Earth trunk code by demon\_test.rb. The code needs to be made robust so it works on Mac and Linux and with different versions of Ruby. This was evidenced by some tests needing to be skipped to make it run in the different environments.
	\item Alex and Cui did not have reports but explained their progress.
	\item Alex's tasks for the milestone are to integrate milestone 1, set up the repository for group 1, write a testing process document and edit the repository usage document.
	\item Cui said that his ticket, ticket 138, had been addressed by Rising Sun Pictures already and more work needed to be done. He was to investigate timing the execution of the queries.
	\item George was to look at the current test cases and write new ones for the milestone 1 code if required. Progress on this is unknown.
	\item Li noted that the group leader should collate the group members' reports ahead of time and bring them in case members cannot attend the meeting. These need to be sent to David and Li 12 hours before the meeting time.
	\end{itemize}
\item Discussion of Tasks
	\begin{itemize}
	\item Query optimisation may be related to how the database schema. Investigation optimising the database may be useful for ticket 138.
	\item Tasks need to be broken down into more detail so that time estimates can be made for sub-tasks. The sub-tasks should be clear and implementable in the given time period.
	\item Documentation of research for tickets or of code experimented with needs to be disseminated throughout the project group to share knowledge.
	\end{itemize}
\end{enumerate}

\end{document}  