\documentclass[10pt, a4]{article}
\usepackage{times}
\begin{document}

\title{Software Engineering Group Project - 7096B}
\author{Semester 2 Week 2 Meeting - Sub-Group 1}
\date{Wed Aug 06, 2008 (13:00hr)}

\maketitle
 
\noindent {\large \textbf{\underline{Minutes of Meeting on Wed Aug 06, 2008}}}\\
 
\noindent \textbf{Attendees:} Dr. Li Jiang, Alex Egan, Filimoni Lutunaika, George Sainsbury, Xiaodong Cui\\

\begin{itemize}
\item Dr. Li commenced the meeting and asked each subgroup member to present their individual progress with the current milestone.
\item Ticket #174: Creating the Earth Gem
\subitem George stated he had not made any progress on his assigned task due to a serious personal injury that he recently sustained. However, he expressed his intention to complete the said task by the scheduled milestonwhere the user could then decidee presentation date next week. He also informed everyone that he plans to complete the relevant documentation subtask after sorting through the various reference materials that he had collected during the previous milestone.
\item Ticket #75: Sort by name or size
\subitem Alex presented his progress on this ticket by stating that he had identified the 'potential' files to be edited. So far, it appears that these files are all part of the 'View' aspect of the Earth web application and he intends to simply use some of the existing class methods in the RSP code base. He expects to complete this ticket by the scheduled milestone presentation date next week.
\item Ticket #131 - Use real disk usage instead of byte size
\subitem Cui presented his progress and mentioned that he had attempted this ticket during the previous milestone. However, Dr. Hemer had suggested that instead of simply converting the units directly in the code, a more elegant solution would be to make the units configurable perhaps on-the-fly and letting the user decide. Further, Cui had completed the conversion of the navigation view and is currently working on the radial view. He also expects to complete the ticket by the scheduled milestone presentation date next week.
\subitem Dr. Li adviced everyone to try and keep track of the time spent on each task as this would be valuable in the planning process of subsequent project milestones.
\item Ticket #186 - Remove Feature of Earth Daemon
\subitem Fili presented his progress on this ticket and mentioned that he had completed the initial substasks 1 and 2, which involved investigating the current implementation of the add feature and identifying components that would have to be modifying in the implementation of the remove feature. He also stated in order to complete these initial subtatsks, it had been necessary to browse through the underlying code 'Model' aspect of the Rails MVC framework and specifically, the ActiveRecord::Base class. He also expects to complete this ticket by the scheduled milestone presentation date next week.
\subitem Dr. Li then made some general enquiries about how familiar or fluent each subgroup member is with Ruby and Ruby on Rails. The subgroup's general response had been that while each member now has some vague idea of the said languange, the relatively flexible syntactic aspect of Ruby on Rails and haml could be a potential source of confusion. Dr. Li then provided some advice on how to tackle this issue and further reiterated that learning a new language quickly is one of the most valuable workforce skills for software engineers.
\end{itemize}

\textbf The meeting ended at 1:40 pm.\\

\textbf{Next Meeting:} Aug 13, 2008 (Wed) @ 1310hr\\

\[\emph{End}\]
 
\end{document} 
