\markright{WONG KEN S'NG (1159155)}
\pagestyle{headings}

\begin{center}
{\large\textbf{\underline{{Ken S'ng's Milestone 6 Report}}}}
\end{center}

\section*{Executive Summary}

I suggested to improve the way the daemon plugins are to be managed, as I find it is not very organized to have a several scripts to manage the plugins. I have created a main script that consolidates all the plugin management scripts (installation, uninstallation and signing). Besides that, I also have added a script to list all the currently installed plugins, as there is no way to know whether what plugins has been installed prior to the script was written. Besides that I provided my assistance to another subgroup to investigate how integration can be done. 

\section*{Tasks and Activities Assigned}

\begin{itemize}
    \item Overseeing the progress of the developments of the plugins mechanism development.
        \begin{itemize}
            \item Plugins deployment retrofitting
                \begin{itemize}
                    \item Description: This task is geared towards retrofitting plugins install scripts from RSP to support the latest additions to the plugins framework.
                    \item Affected files: \texttt{script/list\_plugins}, \texttt{script/earth\_plugins}, \\ \texttt{lib/earth\_plugins\_interface/plugin\_manager.rb}
                    \item Git commits: \texttt{(pamalite/earth) 96828da9db7b7c5f19ac67f0b336727052d18b9e}
                    \item Estimated time taken (planned): 5 hours
                    \item Estimated time taken (actual): 4 hours
                \end{itemize}
        \end{itemize}
    \item Helping out on pre-integration investigation and analysis.
        \begin{itemize}
            \item Description: This is not outlined in the M6 plan. I was engaged to help out on figuring out how to use \texttt{git} to merge all the subgroup repositories as a preliminary step before the actual integration begins. 
	         \item Idea/Solution: N/A
	         \item Affected files: N/A
	         \item Git commits: \textit{Not relevant as the commits done were experimental.}
	         \item Estimated time taken (actual): 3 hours
	     \end{itemize}
\end{itemize}

\section*{Resource Contributions}

For this milestone, I have estimated that I had spend about 12 hours (including 5 hours meeting time) over the spread of 3 weeks. I have budgeted 45 hours (15 hours per week) for this semester. The other 15 hours were spend on my research project. 

Looking at the hours I felt that I have had a productive sprint, though I am only using a fraction of my budgeted hours. The rest of the hours were used for other academics commitments. However, I managed to further integrate the group to get the daemon and GUI plugins retrofitted and implemented, respectively. Besides that, though being the main contact of the group, I still get to do some coding to help the group further, and lend my assistance to the other subgroup on the integration preliminaries. 

\section*{Rooms for Improvement}

\begin{itemize}
   \item Better time estimation needed for paper work and small coding parts. Previously, the budgeted time was huge as there were a lot of things needed to be done. However, it became a habit to give huge budget, and for this sprint, where the main aim is to prepare for the finishing of the project, only required minimal budget. I should give more time for paper work for this sprint. 
\end{itemize}
