\markright{Kun Zhou(1154356)}
\pagestyle{headings}

\begin{center}
{\large\textbf{\underline{{Kun Zhou's Milestone 6 Report}}}}
\end{center}

\section*{Executive Summary}

In this milestone, following the progress of research about GUI plugin system, we decided to realize it by two different ways: one is using the plugin system of rails; the other one is using the plugin manager created by ourselves. Therefore, on one hand, I and Cui focused on the first way; on the other hand, huang realized plugin manager. The customer could choose the better way they thought between these two. I changed the ticket about metadata into plugin. Most of the time was spent on the problem about the view part. Now we got a great progress on it. 

\section*{Tasks and Activities Assigned}
\begin{itemize}
    \item Rails plugin research
        \begin{itemize}
            \item Sub-task 1: Analyse the rails plugin stuff Cui created in previous milestone
                \begin{itemize}
                    \item On the researh on rails plguin, i have to keep steps with Cui by analyzing the rails plugin stuff which was created by Cui in previous milestone. That is about user usage. It covered database and some front end. So that it is the best way to master the method of creating rails plugin.
                    \item Estimated time taken (planned): 10 hours
                    \item Estimated time taken (actual): 14 hours
                \end{itemize}
            \item Sub-task 2: Follow the tutorial on website and research on rails plugin development
                \begin{itemize}
                    \item After analyzing the created plugin, I found that is not enough for solving new problem and realization of new requirement. Therefore, I searched on the internet and got some material, which are papers about rails plugin development.
                    \item Estimated time taken (planned): 15 hours
                    \item Estimated time taken (actual): 20 hours
                \end{itemize}
        \end{itemize}
    \item Create new plugin for metadata
        \begin{itemize}
            \item Sub-task1: Create files about controller, view and model
                \begin{itemize}
                    \item It is easy for me by following the guider from internet. 
                    \item Estimated time taken (planned): 5 hours
                    \item Estimated time taken (actual): 6 hours
                \end{itemize}
            \item Sub-task 2: Polish functionality about view part
                \begin{itemize}
                    \item In the previous milestone, for view part, table can be created by new line addition in some particular application file. In the milestone, search field can be created. Additionally, those two can be created automatically without adding new line.		
                    \item Estimated time taken (planned): 18 hours
                    \item Estimated time taken (actual): 26 hours
                \end{itemize}
        \end{itemize}
    \item meeting and discussion
        \begin{itemize}
            \item In this milestone, most of work need teamwork and cooperation. For this reason, we took a lot of time on meeting and discussion. That is the base of progress.
            \item Estimated time taken (actual): 10 hour
        \end{itemize}
\end{itemize}

\section*{Resource Contributions}

In this Milestone, I spent a lot of time on the analysis of plugin and solution of some new requirement almost 50 hours. Most of the other hours were mainly spending on working with my group member. But after this milestone, I have a whole structure of rails plugin system and understand the way it works.

\section*{Rooms for Improvement}


The first problem in this milestone for me is my lacking of experience of development about earth daemon. Fortunately, i have passed and got a lot of skills. It should be improved in the future. Additionally, I cost too much time on solution of a particular problem and tried to gain it individually. I should have sent it to the whole group and discusses with the others. It should be a better way to conquer the wall of difficulties.
