\documentclass{article}
\usepackage{a4wide}

\begin{document}
\markright{Yang Qing (1156611)}
\pagestyle{headings}

\begin{center}
{\LARGE\textbf{\underline{{Individual Milestone 6 Report}}}}
\end{center}

\section*{Executive Summary}
In this milestone, I was assigned to work on the plugin installation. I spent the first week in understanding the concept of Mohhamod's extension point. In the second week,I was working on upgrading the install script for adapting to Mohhamod's extension point and implementing the uninstall script. In the last week of this sprint,Ken told me that I need to think about the dependancies among plugins. However, due to time is not enough and after discussing with Mohhamod, we decided to complete everything within the first week of milestone 7.


\section*{Tasks and Activities Assigned}

\begin{itemize}
    \item Understanding the concept of extension point and understanding how extension points work in earth.
        \begin{itemize}
            \item Sub-task 1: Have a research on what is extension point. 
                \begin{itemize}
                   \item Description: Due to not know the concept of extension point, I read the documentation written by Mohhamod and searched some related information from Internet,so that I can understand what is extension point properly.
                   \item planed time taken :15 hours\\
                   \item actual time taken :15 hours\\
                \end{itemize}
            \item Sub-task 2:Learning about how extension points work in Earth
                \begin{itemize}
                    \item Description: Reading all the code in earth related to extension point so \\  as to understand how the code works 
                    \item planed time taken :15 hours\\
                    \item actual time taken :10 hours\\
                \end{itemize}              
            \item Upgrading install script ,creating and implementing uninstall script
                \begin{itemize}
                    \item Sub-task 1:  Upgrading install script
                        \begin{itemize}
                            \item Description:modifing code in the method called install\_from \_file() in plugin\_manager and modifing code in the script of\\        install\_plugin to make the installation adept to extension points.\\
                            \item planned:10hours\\
                            \item actual: 5hours
                        \end{itemize}
                    \item Sub-task 2: implementing uninstall script\\
                        \begin{itemize}
                            \item Description: creating uninstall\_plugin.rb in script and a method called\\ 
                            uninstall plugin in plugin\_manager\\
                            \item planned:5hours
                            \item actual: 5hours
                        \end{itemize}
                \end{itemize}
            \item communicate with group members 
                \begin{itemize}
                    \item Sub-task 1: communicate with group members to see if I did my job properly.
                        \begin{itemize}
                            \item Description: I attached my code in email and sent to my group members. I asked for suggestions from Ken and Mohhamod. Finally we agreed on that the install script got no problem, but we need to polish the uninstall script. The dependances need to be considered.And discussed about how to implement it.
                            \item Estimated time taken (planed): 20hour
                            \item Estimated time taken (actual): 20 hour
                        \end{itemize}
                \end{itemize}
        \end{itemize}
\end{itemize}

\section*{Resource Contributions}

For this milestone, I have estimated that I had spend about 70 hours (including  meeting hours over the spread of 3 weeks).

\section*{Rooms for Improvement}

\begin{itemize}
   \item In this milestone, everything went on very well. The communication had been improved quite a lot compared with last milestone.
\end{itemize}
\end{document}
