\documentclass{letter}

\begin{document}

{\large \textbf{\underline{Agenda for meeting on 14$^{th}$ October, 2008 at 1300 hours}}}\\

\textbf{Attendees:} Mohammad, Jian Huang, Keane, Fil, Ida, Xiaodong, David Hemer, Jiang Li \& Ken S'ng Wong \\

\textbf{Contents:}

\begin{enumerate}
    \item Milestone 6 postmortem
        \begin{itemize}
            \item What have we done right?
            \item What needs to be improved?
        \end{itemize}
    \item Milestone 7 planning
        \begin{itemize}
            \item Week 1: Cleanup and documentation. 
                \begin{itemize}
                    \item Daemon plugins
                        \begin{enumerate}
                            \item Get the deployment scripts polished. 
                            \item Document the process from RSP's own plugin to the current version. 
                            \item Finish up any unfinished implementations.
                        \end{enumerate}
                    \item GUI plugins
                        \begin{enumerate}
                            \item Polish up the standards and steps deploy plugins. 
                            \item Document the investigations process and how plugins can be developed and deployed by the user. 
                            \item Finish up any unfinished implementations. 
                        \end{enumerate}
                \end{itemize}
            \item Week 2: Continue with cleanup and documentation, and open up resources to the entire group for integration. 
            \item Week 3: Finalize all codes and documentations, and hand the project back to RSP.
        \end{itemize}
    \item Recognitions
        \begin{itemize}
            \item Ken to Xiaodong, Keane and Huang Jian for their job well done on getting the GUI plugins from POC to practical implementation. 
            \item Ken to the group for being the most collaborative sprint. 
        \end{itemize}
    \item Opens
\end{enumerate}

\end{document}  