\documentclass{letter}

\begin{document}

{\large \textbf{\underline{Meeting Minutes Taken on 26$^{th}$ May, 2008 at 1500 hours}}}

\textbf{Attendees:} Ken, Hill, David, Sahil, Li \& Jon 

\textbf{Excused:} Hemant

\textbf{Next Meeting:} 27/05/2008 (Tuesday) @ 0800 hours 

\textbf{Contents:}

\begin{enumerate}
\item Milestone 2 Postmortem
	\begin{itemize}
		\item Database Studies (Owner: Hill)
			\begin{itemize}
				\item The time taken to study the database was reviewed.
				\item It was found that most of the time was not spend on understanding the database, but rather to learn how to format the document using LaTeX. 
				\item Hill said that he used about 6 hours spanned across 6 days for this task, and most of it were spend on LaTeX. 
			\end{itemize}
		\item Ticket 27 (Owner: Sahil)
			\begin{itemize}
				\item Sahil promised to have this ticket delivered by Friday (30/5/2008).
				   \item The main reason for the delays was due unexpected hardware failures and unresolved personal issues. 
			  \end{itemize}
		 \item Ticket 66 (Owner: Ken)
		 	  \begin{itemize}
			  		\item This has been unit tested and it is now declared closed, from the perspective of this group project. 
					\item The only thing left is the approval from RSP.
			  \end{itemize}
		 \item Ticket 23
		 	  \begin{itemize}
			  	    \item Jon commented that somehow the implementation of the ticket overlapped with Group 2's ticket on metadata. 
				    \item David apologized for confusing the idea between tagging and metadata. 
			  \end{itemize}
	     \item Resources and planning
	         \begin{itemize}
	         	    \item Ken commented that due to bad organization and priority screw-ups, Milestone 2 had not been as productive as Milestone 1. 
		           \item David commented that it seems like most members had de-prioritzed the project for other academic commitments. Also, we were lacking in breaking tasks into smaller subtasks that can be done in parallel. 
	         \end{itemize}
	\end{itemize}
\item Milestone 3
    \begin{itemize}
        \item Plugin System
             \begin{itemize}
             	    \item It was recommended by David that we should start looking at file\_monitor as a plugin. Then, create hooks in the core system to the plugins. 
	               \item Also, it was suggested that the group should look into whether is it possible to create plugins for views, controller and model. 
	               \item The deliverable by the end of this milestone is to get some simple plugins implemented as a demo. Also, have the system documented. 
             \end{itemize}
    \end{itemize}
\item Opens
    \begin{itemize}
        \item David reminded that we should keep track the time used to attend to the tasks set in the project. 
    \end{itemize}
\item ARs
    \begin{itemize}
        \item Review the database documentation done by Hill. (Owner: Ken) (Due: 2/6/2008)
        \item Plan for Milestone 3 (Owners: All) (Due: EOD 27/5/2008)
    \end{itemize}
\end{enumerate} 
\end{document}  