\documentclass{letter}

\begin{document}

{\large \textbf{\underline{Meeting Minutes Taken on 27$^{th}$ May, 2008 at 0800 hours}}}

\textbf{Attendees:} Ken, Hemant, Sahil \& Jon 

\textbf{Excused:} Hill

\textbf{Next Meeting:} 02/06/2008 (Monday) @ 1500 hours 

\textbf{Contents:}

\begin{enumerate}
\item Earth plugin system brainstorm
	\begin{itemize}
		\item Major tasks were first laid out as the blueprint for Milestone 3.
			\begin{itemize}
				\item Study of existing plugin architecture
				\item Formalizing the plugin development specifications - eg: protocols and standards
				\item Prototyping the expected plugin system 
				\item Developing dummy plugins as examples
				\item Creating test cases for plugin system - Will the system break because of a sabotage?
				\item Documenting the architecture
			\end{itemize}
		\item From the major tasks, they were broken down into smaller and manageable tasks.
			\begin{itemize}
				\item Study of existing plugin architecture
					\begin{itemize}
						\item The group agreed to study the architecture in parallel from different POV - one from earthd through file\_monitor, and the other is only studying the plugin\_manager. 
						\item This strategy is to gather as much information about the plugin setup of the system and normalize the findings after the initial exploration.
						\item Two pairs of groups were assigned for the separated exploration. 
					\end{itemize}
				\item Prototyping the expected plugin system
					\begin{itemize}
						\item The group agreed that the prototyping will be broken down to smaller tasks after the initial exploration.
					\end{itemize}
			  \end{itemize}
		\item A reality check was done on the time given for this milestone
			\begin{itemize}
				\item The group agreed that with the tasks gathered, it seemed like the group is over-committing on the goals and deliverables. 
				\item It was found that many of the group members have given this milestone a lower priority due to other academic commitments.
				\item The strategy was to assigned two or more member to a task for a single person to free up the time for the members to attend to other academic commitments. That means, the pair will take as much time as a single person take. 
				\item Also, certain major tasks were marked as Zero Budget Baseline (ZBB). That means, tasks that had been ZBB-ed will be binned for the next sprint or when more time is allocated to complete them. The following are the tasks that had been ZBB-ed: 
					\begin{itemize}
					\item Creating test cases
					\item Formalizing plugin development specifications 
					\end{itemize}
				\item The reason for ZBB-ing the listed tasks as they will push the prototyping tasks out of this milestone. 
			\end{itemize}
	\end{itemize}
\item Pair allocations
	\begin{itemize}
		\item Pair 1: Sahil \& Hemant
		\item Pair 2: Jon, Ken \& Hill
	\end{itemize}
\item ARs
	\begin{itemize}
		\item Study plugin\_manager with file\_monitor - Sahil \& Hemant - Due: 02/06/2008
		\item Study plugin\_manager without file\_monitor and as a generic system - Jon, Ken \& Hill - Due: 02/06/2008
	\end{itemize}
\end{enumerate} 
\end{document}  