\documentclass{letter}

\begin{document}

{\large \textbf{\underline{Meeting Minutes Taken on 14$^{th}$ May, 2008 at 1500 hours}}}

\textbf{Attendees:} David, Ken, Hill, Sahil \& Jon 

\textbf{Absent:} Hemant 

\textbf{Next Meeting:} 19/05/2008 (Monday) @ 1500 hours 

\textbf{Contents:}

\begin{enumerate}
	\item Progress Update
		\begin{itemize}
			\item Earth installation
				\begin{itemize}
					\item So far everyone got it installed on their own personal machines. However, due to unexpected hardware failures, it is slowing progress down.
					\item The members who are facing such problems are currently working on it and committed to get their work done by end of this week. 
				\end{itemize}
			\item Database studies
				\begin{itemize}
					\item Sahil \& Jian Huang presented the first draft of ERD
					\item David suggested that for the second draft, we should be looking closer into the usage of the schema and have them documented. 
					\item David also suggested for us to start on building a Data Dictionary. 
				\end{itemize}
			\item Ticket 27
				\begin{itemize}
					\item Due to unexpected hardware failure, the ticket is currently redone by Sahil.
				\end{itemize}
			\item Ticket 66
				\begin{itemize}
					\item Ken is currently looking at how to test this ticket. 
				\end{itemize} 
			\item Ticket 23
				\begin{itemize}
					\item Jon presented the data structure of the tagging mechanism.
					\item David suggested to post a question on Trac to clear up the confusion between normal tagging and RSP convention tagging from metadata.  
				\end{itemize}
		\end{itemize}
	\item Plans moving forward
		\begin{itemize}
			\item Testing and Test Coverage
				\begin{itemize}
					\item Ken is currently looking at both. He is also trying to find out how to test Ticket 66.
					\item Sahil will look at testing for Ticket 27.
					\item Jon will look at testing for Ticket 23.
				\end{itemize}
			\item Synching of git repo
				\begin{itemize}
					\item Subgroup 3 git repo has been created and made public.
					\item All members can now clone the repo and push and pull updates.
				\end{itemize}
		\end{itemize}
	\item Opens
		\begin{itemize}
			\item David re-assured the special purpose machines will be setup ASAP.
		\end{itemize}
	\item ARs
		\begin{itemize}
			\item Jian Huang will come up with the 2$^{nd}$ draft of the database document. (Due: 21/05/2008)
			\item Ken to find out how to properly test ticket 66 (Due: 19/05/2008)
			\item Jon to complete the first prototype of Ticket 23 (Due: 21/05/2008)
			\item Sahil to find out how to properly test ticket 27 (Due: 19/05/2008)
		\end{itemize}
\end{enumerate} 
\end{document}  