\documentclass{article}
\usepackage{a4wide}
\usepackage{graphicx}
\pagestyle{headings}

\begin{document}
\title{\textbf{Milestone 4 Report for Group 2}}\author{Ming Jie Tan \\ Yang Qing }

\maketitle
\thispagestyle{empty}
\newpage{}

\thispagestyle{empty}
\tableofcontents
\newpage{}

\setcounter{page}{1}
\section{Introduction}

Below are the reports for the group as a whole and two individual reports.

\section{Report - Group Summary}

\subsection{Investigation of Tickets}
At the start of the development iteration each member was effectively assigned a task to complete for this period. During the first week investigation and research of the task provided was done.
\subsection{Planning of the Group's Tasks}
Given the tasks that were decided upon, a plan was set out in order to determine how each member would roughly spend their time working on the tasks assigned to them. From this we were able to estimate how long the various tasks would take and determine whether the likelihood of task completion would be possible during this time period.
\subsection{Testing of the Group's Tasks}
Given the split of the task, group members were able to complete their individual sections. As a result of the nature of individual tasks, most of the testing conducted during this period was individual testing of their own code.
\subsection{Review}
Overall during this iteration, a number of new tickets were undertaken, with some improvements made on the ticket of the previous milestone. The group managed to make good progress into the tasks that it was given, but currently some tasks are not quite completed. Looking forward with the much larger task of the plugin system requiring more time, a number of members are likely to move onto development of that system. With respect to how much time was put into the project, each member put in a significant amount of time in order to complete the tasks required of them. The time split for this iteration definitely was dominated by research and documentation as most of the tickets undertaken were new and required more time spent on research.

\newpage{}

\section{Report - Ming Tan}

During this iteration, I took on a few different tasks, but this period was mostly ended up in research. Initially this milestone begain with some planning to determine what tasks to undertake.

\subsection{Investigation}

At the start of this development cycle, I initially investigated ticket 174 with Callum, before a consult with Ken resulted in us dropping this ticket as the plugin system was being revamped. Following up on this, after looking at several other tickets that could be undertaken, we decided to look at ticket 29 and investigate more into acquiring image data.

\subsection{Planning}

Following the meeting to decide what each group would undertake as tasks for this iteration, I sketched up a general task flow for the various tasks that each group would be undertaking. I updated the plan for milestone 4 for the group. Following this I sketched up a plan for the tasks that I would need to undertake in order to complete my tasks for this iteration.

\subsection{Coding and Documentation}

Although no code was actually implemented during this phase, I did complete some documentation in order to update the planning. However there was some investigation in terms of determining how to process image data and how to retrieve it.

\subsection{Time Spent}

I would estimate that each week, I spent around 6 hours on average on the project. During the first week aside from meeting time and preparation, most of my time was spent reading the code and trying to understand what would be required for tickets 174. The second week of the iteration, I allocated a bit more time toward investigating the new task (Ticket 29). The remaining time that I had was spent researching ticket 29 and discussing with callum how best to proceed with the task.

\newpage{}

\section{Report - Yang Qing}


Since milestone 4 was the first milestone in the new semester, I spent a lot of time on preparation, which includes getting the earth installed and reviewing the work that was done in last semester. \\
\\
Due to the GUI environment of my Linux was broken, I had to reinstall Linux and Earth. However, the latest version of rails had many new features. It means if installing it as before, the earth would not work properly. Therefore many weird errors appeared during the process of my earth installation. Then I found that several new packages were required and the openssl under the repository of ruby/ext should be installed. Anyway, it took me a long time to fix the problem.   \\
Actual working time: 20+.\\
\\
For milestone 4, my task was to edit documentation in wiki, which was required by ticket #141. In terms of the requirement, I put a description about the architecture of earth and how earth worked under the ruby-on-rails MVC framework in wiki. And I attached a graph about the relationships among each part of earth in the attachment. It seems like an easy job. However, I spent a lot of time on reading and researching.  Actual working time: 30+.\\
\\
Furthermore, I spent about 20 hours on some other things, such as reviewing my work in last semester and making all kinds of research on ruby on rails and earth. \\
Actual working time:15+.\\
\\
Above is a summery of what I did in milestone 4. \\
\\
\end{document}
