\begin{center}
{\textbf{\underline{{Jian Huang Milestone 4 Report}}}}
\end{center}

\section*{Executive Summary}

Research on Plugins. Aftering semester 1, I found almost plugin system use APIs, but, so far, most of us have done some tickets, which means that if using APIs, we need to redo what we've done. Therefore, I compare some other skills. Two main techniques of them are Method 1: Use code, which can run itself and Method 2: APIs.

\section*{Tasks and Activities Assigned}

\begin{itemize}
	\item Method 1 Use code.
	     \begin{itemize}
	        \item Sub-task 1: Look at how it works in ruby on rails.
	           \begin{itemize}
					\item Description: The function can be used in any tickets. When tickets are installed in earth, the function will run firstly and then trigger the main functions in the ticket. So ticket can run itself.
					\item Idea/Solution: Search wheter there is function like other languanges, Java or C++, that can use directly, or we need to build it ourselves. 
					\item Estimated time taken (planned): N/A hours
					\item Estimated time taken (actual): N/A hours
				\end{itemize}
			\item Sub-task 2: Solve the security issue.
			   \begin{itemize}
					\item Description: There is a security issue in this way, and some tickets have mentioned that we need to think about which part of earth coding we can expand and / or extend. 
					\item Idea/Solution: Set privilege, or protect function to avoid illegal action.
					\item Git commits: Spend lots of time on it, and, unfortunately, have on idea about it.
					\item Estimated time taken (planned): N/A hours
					\item Estimated time taken (actual): N/A hours
				\end{itemize}
	     \end{itemize}
	\item Method 2 API2.
	     \begin{itemize}
	         \item Make structure on earth.
	            \begin{itemize}
	              \item Description: Set earth structure and express how other ways are not good enough to solve our problems. 
					\item Idea/Solution: Discuss it with other group member to get same idea and answer their questions.
					\item Affected files: N/A
					\item Git commits: N/A
					\item Estimated time taken (planned): N/A hours
					\item Estimated time taken (actual): N/A hours
				 \end{itemize}
	         \item Sub-task 2: Publish standards and API
	            \begin{itemize}
				    \item Description: Set three main parts up-level: front-end, back-end, database
					\item Idea/Solution: rebuild file\_monitor 
					\item Affected files: N/A
					\item Git commits: N/A
					\item Estimated time taken (planned): N/A hour
					\item Estimated time taken (actual): N/A hours
				 \end{itemize}
	     \end{itemize}
	\item Rebuild file\_monitor
	     \begin{itemize}
	         \item Description: Set an example on how to use APIs to create plugin. 
	         \item Idea/Solution: Divide it into several basic functions
	         \item Comments: Divide file\_monitor into several defferent basic functions, no matter which of privilege it is in the file\_monitor. However, I change mind again, when nearly finishing, and use the next skill). Set file\_moniter as a up-level package to control database. Do the new code with ken and test it.
	         \item Estimated time taken (actual): N/A hours
	     \end{itemize}
	\item Discuss with other MSE students
	     \begin{itemize}
	         \item Description: See whether we need to rebuild subgroup to do our MSE project. 
	         \item Idea/Solution: Make us more effectional and more ambitional
	         \item Comments: Most of us eager to rebuild.
	         \item Estimated time taken (actual): N/A hours
	     \end{itemize}
	\item Research on the Gui. 
	      \begin{itemize}
	         \item Description: Ruby is different from Javascrip and Asp, and observer part can meet problem to use APIs.
	         \item Idea/Solution: Talk with friends, search info from webpage.
	         \item comments: Find problem, try to solve it.
	         \item Estimated time taken (actual): N/A hours
	     \end{itemize}
\end{itemize}

\section*{Resource Contributions}

No idea how to write this part.

\section*{Rooms for Improvement}

I need to estimate time and try to show more what I have done, especially coding.
