\documentclass{article}
\usepackage{a4wide}
\usepackage{hyperref}

\begin{document}
\markright{SEGP2 Group 3 (18$^{th}$ August, 2008)}
\pagestyle{headings}

\begin{center}
{\textbf{\underline{SEGP2 Group 3 Milestone 4 Report}}}
\end{center}

\noindent{\textbf{Total Hours Spend:} approx. ... hours}

\section*{Executive Summary}

Milestone 4 began by reviewing the findings from Jian Huang's research into various plugins frameworks adopted by other software projects. The decision to take the path of converting the existing Earth plugins architecture (code inclusion) to the proposed API (Application Programming Interface) plugin architecture. The group had agreed not to work any tickets as this task is expected to be heavy and will relinquish all the budgeted hours. 

Both Huang and Ken took up the task for laying the groundwork for the API framework. Since this is supposedly a continuation from Milestone 3, and Ken were not present during Huang's presentation on the proposed API framework, both of them had spend most of the time trying level out expectations on the tasks taken. Unfortunately, constant communication failures, and personal and academics commitments had plagued this pair from moving forward as quick as expected. Ken had expressed that he had spend about 53 hours in this milestone, while Huang had estimated he had contributed ... hours this sprint. 

While both the MSE members were busy working on the API framework base, the BE(SE) members worked on other aspects of the project. Jon had volunteered to take over the administrative tasks of the group. Besides that, it was planned to have both Jon and Sahil to explore the front-end of Earth and try to get the same API concept applied onto the front-end. However, Sahil ``isolated'' himself from the group and was not able to provide progress updates to the group, which forced Jon to work alone, while consulting both Ken and Huang when doubts arises. Overall progress from Jon had been good, where he already had an idea what and how should the front-end API should be done. Jon had reported that he had spend ... hours in this sprint, inclusive of all the hours taken for administrative work. Unfortunately, the group does not know how much time Sahil had spend on any aspect of this project, as of the time of this report is written. 

Milestone 4 can be considered as another unproductive milestone. This is because there is no solid plugin prototype developed and presented, which was the expected deliverable during planning time. The following are the key takeaways of this sprint for this group:

\begin{itemize}
	\item \textbf{Lack of member commitments:} It was observed that other academic commitments (research project and course assignments) and personal commitments (waged work) had affected the overall performance of the members of this group. For one case, no work has been done at all.
		\begin{itemize}
		   \item Plan: To stress the importance of this project to be delivered back to a real customer (RSP) and lack of commitments will not only discredit ourselves, also the school in general. 
		\end{itemize}
	\item \textbf{``Do more with less'' is difficult to achieve:} It was planned and discussed that the we, as a group, will not be affected by the decreasing number of head count. The group agreed to strived to do more with less, but not committed after each member had been swamped with other commitments. Also, this strategy is related to the previous takeaway. 
		\begin{itemize}
			\item Plan: Put forth this problem to the full group and had it solved by everyone by the upcoming meeting.
		\end{itemize}
\end{itemize}

\section*{Individual Reports}

Attached are the individual reports of each member of the group. 

\include{a1159155.1}

\end{document}  