\documentclass[10pt, a4]{article}
\usepackage{times}
\begin{document}

\title{Software Engineering Group Project - 7096A}
\author{Semester 1 Week 10 Meeting - Sub-Group 1}
\date{Wed May 21, 2008 (1400hr)}

\maketitle
 
\noindent {\large \textbf{\underline{Minutes of Meeting on Wed May 7, 2008}}}\\
 
\noindent \textbf{Attendees:} Dr. Li Jiang, Alex Egan, Filimoni Lutunaika, Xiaodong Cui\\
\textbf{Apologies:} George Sainsbury\\

\begin{enumerate}
\item Progress Reports
  \begin{itemize}
  \item Cui described his progress with Ticket 138 on the optimisation of query under radial view. The issue had been addressed to some extent by Rising Sun Pictures but the active status of the said Ticket probably indicated that further work is still being considered. He would be undertaking further investigation by making some standard performance measurements to verify the optimality of the current query implementation.
  \item Fil presented the status of his investigation of Ticket 146 which involves the continuous testing of the Earth trunk code by \emph{daemon\_test.rb}. The testing script was working but further investigation was being considered on how to conveniently configure the tests on the fly via the terminal or an appropriate user interface.
  \item Alex's tasks for the current milestone(M2) are to integrate the outcomes of Milestone 1, setup the subgroup repository for Group 1, write a testing process document and edit the repository usage document.
  \item George was investigating the current test cases and its appropriateness for verifying the codes from Milestone 1. Progress was unknown due to George's absence from the meeting.
  \item Li noted that the group leader should collate the group members' reports ahead of time and submit them in case a member cannot attend the meeting. These reports together with the meeting agenda need to be sent to David and Li at least 12 hours before the scheduled meeting time.
  \end{itemize}
\item Discussion of Tasks
  \begin{itemize}
  \item Query optimisation may be related to the underlying physical schema of the database. Investigation into optimising the database schema may be required for Ticket 138.
  \item Tasks need to be broken down into more detail so that time estimates can be made for sub-tasks. Also, the sub-tasks should be clear and implementable within the given time period.
  \item Findings from the ticket investigations and the associated code implementations need to be promptly disseminated throughout the entire project group to ensure the currency of available knowledge.
  \end{itemize}
\end{enumerate}

\textbf{Next Meeting:} May 21, 2008 (Wed) @ 1400hr\\

\[\emph{End}\]
 
\end{document} 
