\documentclass{article}

\begin{document}

{\large \textbf{\underline{Subgroup 3 Milestone 3 Plans}}}

\section{Tasks Assigned}

Beginning of Milestone 3, we were assigned the following tasks:

\begin{enumerate}
	\item Ticket 27 - MIME-type
	\item Studying of the Earth Plugin System
\end{enumerate} 

\section{Resources}

We currently have five members that consists of 2 BE(SE) and 3 MSE students. Please refer to the m3\_schedules.pdf file for resources availability details. 

\section{Tasks Allocations}

We have broken down the tasks into smaller subtasks that will be carried out in pairs or smaller groups. 

\begin{enumerate}
	\item Ticket 27 will be completed by 30$^{th}$ May (Friday) by Sahil
	\item Study file\_monitor and plugin\_manager (ETA: 5 hours)
		\begin{enumerate}
			\item Pair 1 (Sahil \& Hemant)
				\begin{enumerate}
					\item Study the plugin flags used in earthd
				\item Try to see whether earthd breaks with tempered file\_monitor
					\item Deliverables: Documentation of findings
				\end{enumerate}
			\item Pair 2 (Jon, Ken \& Hill)
				\begin{enumerate}
				\item Study the plugin\_manager from another POV
				\item Try to see how hooks can be made for the system in general
					\item Deliverables: Documentation of findings
			\end{enumerate}
		\end{enumerate}
	\item Create hooks
		\begin{enumerate}
			\item How to install \& uninstall plugins (ZBB)
			\item Hooks will be proposed from both Pair 1 and 2
			  \item Deliverables: Proposals of hook locations by both pairs.
		\end{enumerate}
	\item Plugins for view (Browser) exploration (ETA: 3.5 hours)
		\begin{enumerate}
			\item This task is assigned to Pair 2, and will either do 
				\begin{enumerate}
					\item Extension of the plugin\_manager (ETA: 1 hour); or
					\item Create a new plugin\_manager (ETA: 2.5 hours)
				\end{enumerate}
			\item Deliverables: Sketch of the specifications of the new or enhanced plugin\_manager.
		\end{enumerate}
	\item Plugin\_manager throwaway prototype \& dummy plugins (ETA: 4 hours)
		\begin{enumerate}
			\item Deliverables: Documentation and demo
		\end{enumerate}
	\item Create test cases (ZBB)
		\begin{enumerate}
			\item Load faulty or rogue plugins to see whether the Earth still stands.
		\end{enumerate}
	\item Documentation (Throughout all tasks)
\end{enumerate}

\section{Timeline}

Please refer to m3\_schedules.pdf for timeline details. 

\section*{Remark}

ZBB (Zero Budget Baseline): Tasks that had been label ZBB means the group had decided there is not enough budget resources to complete the tasks. It can be completed when there is more budget given. 

\end{document}  