\documentclass{letter}

\begin{document}

{\large \textbf{\underline{Steps to Setting Up Earth 0.2 on Mac OS X Leopard and maybe Linux}}}\\

\begin{enumerate}
\item Stuffs that you need
	\begin{itemize}
	\item UN*X-based operating system (I'm not sure whether the daemon will work on Windows PC, or not)
	\item SVN to download the latest revision of Earth
	\item PostgreSQL database server + optional db tools
	\item git to prepare for repository
	\end{itemize}
\item Assumptions
	\begin{itemize}
	\item Ruby and Rails are already pre-installed in Leopard. 
	\item This instruction sheet is based on the factory configuration of Ruby on Rails on Leopard. 
	\end{itemize}
\item Install PostgreSQL
	\begin{enumerate}
	\item Download PostgreSQL from {\tt http://www.postgresqlformac.com/server/}. 
	\item Follow the instructions at {\tt http://www2.russbrooks.com:8080/ \\ 2007/11/4/install-postgresql-on-mac-os-x-10-5-leopard}
	\end{enumerate}
	NOTE: You can ignore the steps about installing pgAdmin and PostgreS Gem. 
\item Get the Ruby Gems
	\begin{enumerate}
	\item Launch Terminal and have your Ruby and Rails updated to the latest version. \\ 
	Type the following into Terminal: \\
	{\tt sudo gem update --system}  \\ 
	{\tt sudo gem install rails} \\ 
	{\tt sudo gem update rake} \\
	{\tt sudo gem install rcov} \\
	{\tt sudo gem install postgres} \\ 
	The first command is to update the overall RubyGems, while the rest are pretty much self-explanatory. 
	\item You can type \\
	{\tt gem list} \\
	to check all the gems you installed. And if you are adventurous, you can try \\ 
	{\tt gem list -r} \\
	to check all available gems on the remote gem server. 
	\end{enumerate}
\item Setup SVN, if you have not.
	\begin{enumerate}
	\item Download and install SVN from {\tt http://downloads.open.collab.net/\\binaries.html}
	\end{enumerate}
\item Setup git
	\begin{enumerate}
	\item Follow the instructions at {\tt http://www.dekorte.com/blog/\\blog.cgi?do=item\&id=2539} \\
	NOTE: The instruction DOES NOT install the latest stable release. Check the releases at {\tt http://kernel.org/pub/software/scm/git/}. The version I got is 1.5.4.4. 
	\item You can skip the part to initialize a repo for now. We will use them once we have the repo from RSP. 
	\end{enumerate}
\item Setting up Earth
	\begin{enumerate}
	\item Go to your development space and checkout Earth from RSP's SVN repository \\
	{\tt svn co https://open.rsp.com.au/svn/earth/trunk earth}
	\item Change directory to the checked out directory.
	\item Do a {\tt grep} command in the {\tt db/migrate} directory for \\ {\tt add\_index :[[a-z]*[:punct:]]* :} \\ that looks for all files containing \\ {\tt add\_index ... :unique} \\ line. 
	\item Replace ``{\tt :unique}" to  ``{\tt :unique => true}" to the end of the {\tt add\_index} lines in all the affected files. This is the typo that causes the migration to fail. \\
	{\sl Thanks to David Hemer.}
	\item Start the database up \\
	{\tt sudo -u postgres postgres -D /Library/PostgreSQL8/data}
	\item Setup databases in PostgreSQL by typing the following commands: \\
	{\tt sudo -u postgres createuser --no-superuser --no-createdb --no-createrole earth} \\
	{\tt sudo -u postgres createdb --owner=earth earth\_production} \\
	{\tt sudo -u postgres createdb --owner=earth earth\_test} \\
	{\tt sudo -u postgres createdb --owner=earth earth\_development}
	\item Back in Terminal, change directory to the root in the Earth directory and type: \\
	{\tt rake db:migrate}
	\end{enumerate}
	NOTE: Once you get passed this point, the rest are pretty much done. You can check out the instructions from RSP at {\tt http://open.rsp.com.au/\\projects/earth/wiki/InstallInstructions-0.2}
\end{enumerate} 
Apologies to Windows members. I do not know how to setup Earth on Windows. Also, apologies to Linux members, I am not really sure whether the steps are identical. \\\\
To install Rails, there is a comprehensive instruction set at {\tt http://www.rubyonrails.org/down} \\\\
Anyway, please feel free to feedback and contribute if you find any issue in this list of instructions. 
\end{document}  