\documentclass{article}
\usepackage{a4wide}

\begin{document}
\markright{SEGP2 Plugin Group (9$^{th}$ September, 2008)}
\pagestyle{headings}

\begin{center}
{\large\textbf{\underline{Plugin Group Milestone 6 Plan}}}
\end{center}

\section*{Executive Summary}

The group had discussed that this sprint will be the best sprint to finish up what was left from the previous milestone, and it is best time to plan out for next sprint, which is mainly reserved for packing up the project with test and integration and deliver it back to RSP. The following are the tasks that had been set by the group:

\begin{itemize}
	\item Finish up the 3$^{rd}$ pillar of plugins: deployment.
	\item Create plugins and apply what was created and set on plugins development into them. 
	\item Front-end plugins union: Finalize and have the plugins framework set. 
\end{itemize}

Like last sprint, this group will continue the ``task-force'' strategy in this sprint. The strategy is actually a modified version of pair programming that allows adequate communication among members to work on a task. 

\section*{Resources and Timeline}

\begin{itemize}
   \item Resources:
		\begin{itemize}
		   \item Ken (Group Representative) [15 hours a week]
		   \item Jian Huang (Advisor) [30 hours a week]
		   \item Fillmoni [30 hours a week]
		   \item Mohammad [30 hours a week]
		   \item Ida Yang [30 hours a week]
		   \item Keane Zhou [30 hours a week]
		   \item Xiao Dong [30 hours a week]
		   \item Total hours a week: 195 hours 
		\end{itemize}
   \item Timeline:
       \begin{itemize}
          \item Start Day: 9$^{th}$ September, 2008
          \item End Day: 10$^{th}$ October, 2008
          \item Duration: 15 days, exception to 14 days due to mid-term break
       \end{itemize}
   \item Accumulated hours: \underline{585 hours}
\end{itemize}

\section*{Tasks and Task-forces}

\begin{enumerate}
   \item Plugins deployment retrofitting
      \begin{itemize}
         \item \textbf{Task-force:} Ida (Lead), Mohammad, Filimoni and Ken
         \item \textbf{Git repo:} \texttt{pamalite/earth}
         \item \textbf{Description:} This task is geared towards retrofitting plugins install scripts from RSP to support the latest additions to the plugins framework.
      \end{itemize}
   \item Plugins creation
      \begin{itemize}
         \item \textbf{Task-force:} (N/A)
         \item \textbf{Git repo:} \texttt{pamalite/earth}
         \item \textbf{Description:} The goal of this task is to create plugins, togather with their required API modules and classes, and install them through the plugins framework that had been set in the previous sprint. This task is undertaken individually who wishes to develop plugins for the daemon.              
      \end{itemize}
   \item Finalize and have the front-end plugins framework set
      \begin{itemize}
         \item \textbf{Task-force:} Cui Xiaodong (Lead), Keane and Jian Huang
         \item \textbf{Git repo:} \texttt{pamalite/earth}
         \item \textbf{Description:} This task is to develop a framework to make the MVC-based front-end pluggable. So far, there have been 3 paths explored and the members agreed to finalize which path to take and create plugins on the path set.  
      \end{itemize}
\end{enumerate}

\section*{Deliverables}

\begin{itemize}
   \item A demonstration of assorted plugins for the daemon. 
   \item A demonstration on the improved plugins deployment scripts.
   \item Individual and subgroup reports.
\end{itemize}

\end{document}  