\documentclass{article}
\usepackage{a4wide}

\begin{document}
\markright{SEGP2 Plugin Group (9$^{th}$ September, 2008)}
\pagestyle{headings}

\begin{center}
{\large\textbf{\underline{Plugin Group Milestone 7 Plan}}}
\end{center}

\section*{Executive Summary}

The group had discussed that this sprint will be the cleanup and integration sprint. It was agreed that there will not be any new developments and creations besides patching up existing bugs. 

Besides cleaning and patching the codes to hand-off, the group is committed to get the related reports and documentations produced. 

And last, but not least, the group also committed to help out in having all the repositories integrated and tested as it is understood that integration plays the biggest part in this phase. 

\section*{Resources and Timeline}

\begin{itemize}
    \item Resources:
        \begin{itemize}
            \item Ken (Group Representative) [15 hours a week]
            \item Jian Huang (Advisor) [30 hours a week]
            \item Fillmoni [30 hours a week]
            \item Mohammad [30 hours a week]
            \item Ida Yang [30 hours a week]
            \item Keane Zhou [30 hours a week]
            \item Xiao Dong [30 hours a week]
            \item Total hours a week: 195 hours 
        \end{itemize}
    \item Timeline:
        \begin{itemize}
            \item Start Day: 13$^{th}$ October, 2008
            \item End Day: 31$^{st}$ October, 2008
            \item Duration: 15 days.
        \end{itemize}
    \item Accumulated hours: \underline{585 hours}
\end{itemize}

\section*{Tasks and Timeline}

\begin{enumerate}
    \item Week 1: Cleanup, Patch-up and documentation
        \begin{itemize}
            \item Daemon plugins
                \begin{enumerate}
                    \item Get the deployment scripts polished. 
                    \item Document the process from RSP's own plugin to the current version. 
                    \item Finish up any unfinished implementations.
                \end{enumerate}
            \item GUI plugins
                \begin{enumerate}
                    \item Polish up the standards and steps deploy plugins. 
                    \item Document the investigations process and how plugins can be developed and deployed by the user. 
                    \item Finish up any unfinished implementations. 
                \end{enumerate}
        \end{itemize}
    \item Week 2: Continue with cleanup and documentation, and open up resources to the entire group for integration. 
    \item Week 3: Finalize all codes and documentations, and hand the project back to RSP.
\end{enumerate}

\section*{Deliverables}

\begin{itemize}
    \item A demonstration of the finalized an polished Earth. 
    \item Documentation of
        \begin{itemize}
            \item \texttt{earthd} plugins investigation, development and deployment
            \item GUI plugins investigation, conceptualization, development and deployment
        \end{itemize}
    \item Individual and subgroup reports.
\end{itemize}

\end{document}  