\begin{center}
{\large\textbf{\underline{{Huang Jian's Milestone 7 Report}}}}
\end{center}

\section*{Executive Summary}
In this milestone, I fix test case for my gui plugin technology and finish my research report. Meanwhile, because we choose rails plugin technology for Earth Gui Plugin, I join the other two members to finish our final presentation.

\section*{Tasks and Activities Assigned}

\begin{itemize}
	\item Test Case
	\item Description: Compared with rails plugin, my way is new. And the one of the benefits of the rails plugin is that it supports developers to test what they code easily.
	\item Estimated time taken (planned):30 hours
	\item Estimated time taken (actual): 30 hours
\end{itemize}

\begin{itemize}
	\item Individual Research Report
	\item Description: Document what I've done. And thank ken for checking my paper.
	\item Estimated time taken (planned):20 hours
	\item Estimated time taken (actual): 15 hours
\end{itemize}

\begin{itemize}
	\item With gui plugin members to fix and develop the way to create plugin for gui, and prepare our presentation. 
	\item Description: Document what I've done.
	\item Estimated time taken (planned):30 hours
	\item Estimated time taken (actual): 25 hours
\end{itemize}

\begin{itemize}
	\item Use rails plugin to try to create my idea.
	\item Description: Rails plugin uses a debating function BaseSend. It destroys the structure of rails. And I try to use my technology to avoid using it.
	\item Estimated time taken (planned):0 hours
	\item Estimated time taken (actual): 0 hours
\end{itemize}

\section*{Project Summary}
In this whole year project, I think I've learned a lot, not only the knowledge on the new web developing languange, ruby on rails, but aslo the way to learn and work in australia. If say that I was confused at the beginning of this project, I have walked through the dense fog at the end.
