\documentclass{article}
\usepackage{a4wide}

\begin{document}
\markright{Qing Yang(1156611)}
\pagestyle{headings}

\begin{center}
{\LARGE\textbf{\underline{{Individual Milestone 7 Report}}}}
\end{center}

\section*{Executive Summary}

This milestone was the final milestone for the Earth project. The first task for this milestone was completing and polishing, so that all the functionalities were implemented properly. The second task is integtation and finishing all the documentation. Finally we prepared for the final presentation.
\section*{Tasks and Activities Assigned}

\begin{itemize}
	\item  
	     \begin{itemize}
	        \item Finishing the uninstall script with depandencies
	           \begin{itemize}
					\item Description: Finishing the functionality of uninstall script with all the dependcies. It means that when a plungin is     removed,all its child-plugins and the related extension point should be removed at the same time.
				
					\item Affected files: \texttt{earth/lib/Earth\_plugin\_interface/plugin\_meneger}
					\item  time taken (planned): 16 hours
					\item  time taken (actual): 14 hours
				\end{itemize}
			
	     \end{itemize}
	\item 
	     \begin{itemize}
	         \item retesting all the functionalities
	            \begin{itemize}
	              \item Description: I tested all the functionalities that I have implemented so far and making sure everything is proper before integratin. 
					\item time taken (planned): 15 hours
					\item time taken (actual): 15 hours
				 \end{itemize}
	     \end{itemize}
	\item Writing comments for all the code that I have written so far.
	     \begin{itemize}
	         \item Description: I wrorte comment for the code that I added to clarify what the code means and how it works, so that other developers will work on it easier.
	        
	         \item time taken (actual): 15 hour
	     \end{itemize}
	\item Preparing for the final presentation
	     \begin{itemize}
	         \item Description: We had meeting for the final presentation, everyone was assigned to present a part related to his/her work. I was assigned to present the part about the installation of deamon plugin.
	       
	         \item time taken (actual): 8 hoursd
	     \end{itemize}

\end{itemize}

\section*{Resource Contributions}

For this milestone, I have estimated that I had spend about 60 hours (including the meeting hours) over the spread of 3 weeks. 


\end{document}  
