\documentclass{article}
\usepackage{a4wide}

\begin{document}
\markright{Kun Zhou(1154356)}
\pagestyle{headings}

\begin{center}
{\LARGE\textbf{\underline{{Individual Milestone 7 Report}}}}
\end{center}

\section*{Executive Summary}

In this milestone which is the last spring of project, following the progress of last six milestones, we decided to integrate all the ticket and the plugin system including daemon part and GUI part. Additionally, for the GUI plugin system, a completed documentation is required, including research and instruction. After that, on friday, there is a final presentation for RSP. Each of us need to introduce the progress of earth in the whole project.

\section*{Tasks and Activities Assigned}
\begin{itemize}
	\item Documentation
		\begin{itemize}
	        	\item Based on the process of GUI plugin system development, a documentation is created. I am in charge with the GUI plugin structure and instruction part. It is very complex to describe the whole structure of GUI plugin system and how to use it. Therefore, a lot of diagrams are attached with the document to make the whole process a little distinct.
			\item Estimated time taken (planned): 15 hours
			\item Estimated time taken (actual): 18 hours
		\end{itemize}			
	\item Integration for GUI plugin
	     \begin{itemize}
	         \item Sub-task 1: Improvement of GUI system structure
	            \begin{itemize}
			\item For the future development, i made a little modification of GUI plugin system before integration. The latest version is very convenient and easy to be understood. This version is the one shown on the presentation and in the document.
			\item Estimated time taken (planned): 5 hours
			\item Estimated time taken (actual): 6 hours
			\end{itemize}
	         \item Sub-task 2: Integration
	            \begin{itemize}
			\item After integration of all the completed tickets and the daemon plugin system, GUI plugin system is integrated as a another branch of earth. The testing did not cost me too much time. Because of the version of postgreSQL, I cannot migrate database correctly. Therefore, I cannot test it completely. Fortunately, the modification is just about the GUI. There is no relationship with new feature of database structure.
			\item Estimated time taken (planned): 18 hours
			\item Estimated time taken (actual): 20 hours
		\end{itemize}
	     \end{itemize}
	\item meeting and discussion
	     \begin{itemize}
	         \item In this milestone, most of work need teamwork and cooperation. For this reason, we took a lot of time on meeting and discussion. That is the base of progress.
	         \item Estimated time taken (actual): 10 hour
	     \end{itemize}
\end{itemize}

\section*{Resource Contributions}

In this Milestone, time management is pretty good. Most of time was mainly spending on integration. Because of the final spring and the progress of previous milestone, the whole work went in plan.

\section*{Rooms for Improvement}

This is the final milestone, improvement is great obviously. Each work was completed almost on time in plan. However, the skill of planning still need to be improved.\\

There are still some problems to solve: Firstly, Rails development is huge. I can't understand such a great structure in just 7 months. Some more research is needed. Secondly, resource management is required to be better. For becoming a good software engineer, I still have to improve the ability Fortunately, I have passed and got a lot of skills. It should be improved in the future. Additionally, I cost too much time on solution of a particular problem and tried to gain it individually. I should have sent it to the whole group and discusses with the others. It should be a better way to conquer the wall of difficulties.


\end{document}  