\documentclass{article}
\usepackage{a4wide}

\begin{document}
\markright{SEGP2 Plugin Group (3$^{rd}$ November, 2008)}
\pagestyle{headings}

\begin{center}
{\textbf{\underline{SEGP2 Plugin Group Milestone 7 Report}}}
\end{center}

\noindent{\textbf{Total Hours Spend:} approx. 339 hours}

\section*{Executive Summary}

Milestone 7, the final milestone for this project, began by reviewing what were the leftover work and issues needed to be addressed. These leftovers are mainly bug fixes and code cleanups. Besides that, the group looked up what sort of documents should be produced and delivered to the customer, Rising Sun Pictures (RSP). Finally, the members had concentrated their resources on integrating the system as a whole. The following were the tasks that had been set by the group at the beginning of the sprint:

\begin{itemize}
    \item \textbf{Week 1}: Cleanup, patch-up and documentation the daemon and GUI plugins design, development and implementation.
    \item \textbf{Week 2}: Continue with cleanup and documentation, and open up resources to the entire group for integration.
    \item \textbf{Week 3}: Finalize all codes and documentations, and hand the project back to RSP. 
\end{itemize}

This is the only sprint that a strict policy of no new designs, research and codings was set, which is mainly a code-freeze throughout the group. This is to ease integration activities, and free up resources to address GIT merging issues that were discovered in the previous sprint. Also, this sprint do not have a formal Gantt as it was agreed to have the members to be self-initiative in assisting integration with the other sub-group. However, there were several deliverables that were planned:

\begin{itemize}
    \item Metadata (GUI \& Daemon plugins) \textit{Mohammad, Keane and Xiaodong}
    \item Daemon status (Daemon plugin) \textit{Filimoni and Mohammad}
    \item File Monitor (Daemon plugin) \textit{Ken, Ida and Mohammad}
\end{itemize}

The deliverables were presented as demonstrations during the final presentation. All three items are related to each other, which are to showcase the improved plugins implementation both in the back-end (the daemon) and the front-end (the GUI). Besides the stated deliverables, new scripts (\texttt{earth\_plugins}, \texttt{list\_plugins} and \texttt{uninstall\_plugin}) were also showcased during the presentation as part of plugins management.

Ken had produced the daemon plugins documentation in this sprint, as part of the documentation tasks assigned. Also, he had helped in producing the GUI plugins documentation as well. Besides documentations, he also assisted in integrating all the works done in previous milestones, and plugins. He helped by planning and strategizing how the mergers should be done with the other core members of the integration as well. He spend about 10 hours this sprint to complete this project. 

Filimoni continued with enhancing the daemon feature by redirecting all status information to the front-end. On top of that, he also assisted in the documentation of plugins as a proof-reader. Another significant contribution from him was the assistance on integration as well. He, togather with Mohammad and Jon, had managed to have their respective repositories integrated into the final branch. He had spend about 91 hours in this sprint. 

Xiaodong and Keane produced the GUI plugins documentation, which presented their thoughts in designing the framework from the ground up. They had spend 42 hours (Xiaodong 24 hours and Keane 18 hours) in having the document written.

Ida pursued with Mohammad to have the \texttt{uninstall\_plugins} script corrected to support dependent extension plugins. This error was discovered by Ken in the previous sprint while testing. He suggested to Ida that this can be fixed by making the script intelligent enough to block the removal activity if the plugin being removed has dependent child plugins extended from it. She spend 14 hours in this sprint to have the script amended. 

Mohammad had spend 60 hours in this sprint reviewing the daemon plugins code and made sure that there is enough and clear comments. He then performed more tests to confirm that the system is working as expected. Finally, he joined the group in integrating all the codes from all groups and individual repositories as part of the merging activity. 
 
\section*{Individual Reports}

Attached are the individual reports of each member of the group. 

\include{a1159155.1}

\include{a1149546.1}

\include{a1154924.1}

\include{a1154356.1}

\include{a1144332.1}

\include{a1156611.1}

\include{a1155488.1}

\end{document}  