\documentclass{letter}

\begin{document}

{\large \textbf{\underline{SEGP2 Milestone 3 Group Report of Subgroup 3}}}

\textbf{Total Hours Spend:} approx. 32 hours

Milestone 3 started with analisis and subdivision of possible tasks related to the plugin systems, and assigned to subgroups.

The following are the progress for each of the members of group 3:

\begin{itemize}
   \item Ken:
      \begin{itemize}
         \item Tasks done:
            \begin{itemize}
             \item Study Views \& Controllers in the context of plugin manager
             \item Propose possible hooking system for Views \& Controllers
             \item Prepare and conduct plugin system tutorial for the group
            \end{itemize}

         \item Progress: Performed a preliminary research on the current plugin system found in Earth. Then, by requests, conducted a tutorial for the group to pass down the findings proposals found during the research. Prepared some documents and diagrams about his understanding on the current plugin systems. He also did some experiments directly on the codes to show how the plugin system should work for the Controllers and Views, while advising the Daemon should follow the same design. 
      \end{itemize}

         
    \item Jonathan:
        \begin{itemize}
         \item Tasks done:
            \begin{itemize}
             \item Research about the hooks
             \end{itemize}
             
         \item Progress: Performed a preliminary research on possible ways to create hooks for Ken's proposal.  Found that a standard way to create plugins using inbuilt functionality of ruby.  However, has not been tested into earth yet.  It differs from Ken's proposal, therefore, no guarantee it can be used
        \end{itemize}
        
        
%        SAHIL, HILL, HEMANT
%        
%        PLEASE FOLLOW ABOVE STRUCTURE AND FILL UP YOUR PROGRESS.  THIS MUST BE DONE, AND PUSH TO GIT TODAY.  DAVID MUST GET A REQUEST TO PULL FROM IT
        
     \end{itemize}
 
 
\end{document}  
