\documentclass{letter}

\begin{document}

{\large \textbf{\underline{Meeting Minutes Taken on 2$^{nd}$ September, 2008 at 1300 hours}}}

\textbf{Attendees:} Huang Jian, Cui, Fil, Ken, Mohammad, Keane, David \& Li Jiang 

\textbf{Late:} Ida

\textbf{Next Meeting:} 09/09/2008 (Tuesday) @ 1300 hours 

\textbf{Contents:}

\begin{enumerate}
\item Progress Updates
	\begin{itemize}
		\item Plugin and extensions loading mechanism in earthd.
			\begin{itemize}
				\item Mohommad demonstrated how extensions can be added easily to earthd and also in File Monitor plugin.
			\end{itemize}
		\item Plugins: File Monitor, metadata \& bogus
			\begin{itemize}
				\item It was agreed that these plugins will be used as demonstration for proof-of-concept during the end of Milestone 5 presentation.
			\end{itemize}
		\item API: Phase 1 completed, currently being reviewed
			\begin{itemize}
				\item Keane and Cui had done some decomposition, and their codes are currently being reviewed. 
			\end{itemize}
	\end{itemize}
\item Next steps (for sprint 6)
	\begin{itemize}
		\item Make earthd able to load dependent plugins.
		 \item Work on GUI plugins using Rails plugin.
		 	\begin{itemize}
				\item David shared his version of the GUI plugin architecture, on the surface, but was turned down by Huang. 
				\item Huang had worked on GUI plugins and shared his version of how the GUI plugin should work. However, his ideas were not accepted until he can prove his version is working. 
				\item David and Li pushed Huang to demonstrate his version in the next meeting, if his version works. 
			\end{itemize}
	\end{itemize}
\item Opens
	\begin{itemize}
		\item No opens
	\end{itemize}
\end{enumerate} 
\end{document}  