\documentclass{letter}

\begin{document}

{\large \textbf{\underline{Meeting Minutes Taken on 9$^{th}$ September, 2008 at 1300 hours}}}

\textbf{Attendees:} Huang Jian, Cui, Fil, Ken, Keane, \& David

\textbf{Absent:} Mohammad

\textbf{Next Meeting:} 16/09/2008 (Tuesday) @ 1300 hours 

\textbf{Contents:}

\begin{enumerate}
	\item Milestone 5 Postmortem
		\begin{itemize}
			\item What we did right?
				\begin{itemize}
					\item Plenty of communication through the Google groups.
					\item Tasks segmentation size was right: the 3 pillars of plugins.
					\item Group's attention are focused. 
				\end{itemize}
			\item What needs to be improved?
				\begin{itemize}
					\item Personal goals and doubts on expectations need to be communicated well.
				\end{itemize}
		\end{itemize}
	\item Plan for Sprint 6
		\begin{itemize}
			\item Task 1: Plugins deployment scripts retrofitting. (Lead by Ida)
				\begin{itemize}
					\item David commented that this task can be undertaken by one person, and resources can be pulled from within group. This is a crucial step to polish up the daemon plugins. 
				\end{itemize}
			\item Task 2: Create plugins (Individual)
				\begin{itemize}
					\item David itemized the goal of this task, as it is vague for now. 
					\item Ken: The goal of this task is to create usable plugins and test the plugins mechanism in full for production use. 
					\item David commented that the step taken to wait for plugins idea is not encouraged as the group has 3 members (Ken, Fil and Mohammad) idling while waiting for the ideas to come through. 
					\item David suggested that the 3 members should brainstorm on the potential plugins and start to work on it, and do not wait for the ideas to come through. 
					\item The group agreed. However, will still let the ideas come through for external inputs. 
					\item David said that he would like to plugins of more complex, relative to the plugins created in the previous Sprint. 
				\end{itemize}
			\item Task 3: Front-end plugins union (Lead by Cui Xiaodong)
				\begin{itemize}
					\item Cui said that this sprint is the best time to pick a path and follow it, no matter good or bad. Currently, there are 3 paths, which have their own strengths and setbacks, and we cannot afford to waste this sprint on exploration on new ways of getting this at least to a proof-of-concept. 
					\item David commented that the deliverable of this task is a functional proof-of-concept. Simple plugins will suffice. There is no need an elaborate system to be done. 
				\end{itemize}
		\end{itemize}
	\item Recognitions
		\begin{itemize}
			\item Ken recognized everyone in the group for making M5 the most productive and collaborative sprint so far in this project. 
			\item David also recognized the group for an excellent job well done. He hoped that to continue to see such progress for the subsequent sprints. 
		\end{itemize}
\end{enumerate} 

\end{document}  