\documentclass{letter}

\begin{document}

{\large \textbf{\underline{Meeting Minutes Taken on 7$^{th}$ October, 2008 at 1300 hours}}}

\textbf{Attendees:} Huang Jian, Cui, Fil, Ken, Keane, Ida, Li Jiang \& David

\textbf{Late:} Mohammad

\textbf{Next Meeting:} 14/10/2008 (Tuesday) @ 1300 hours

\textbf{Contents:}

\begin{enumerate}
    \item Progress updates
        \begin{itemize}
            \item Ida \\ 
                    Daemon installation script has been updated \\
                    Uninstall script has been introduced
            \item Ken \\
                    Introduced \texttt{list\_plugins} script to list currently installed plugins \\
                    Introduced \texttt{earth\_plugins} script as the unified daemon plugins manager
            \item Fil \\
                    Daemon status can now be viewed in the browser instead of having to type the \texttt{status} command through a daemon plugin. 
            \item Mohammad \\
                    File metadata extension point is currently being developed.
            \item GUI plugin \\
                    Xiaodong, Keane and Huang Jian briefed and demoed their functional plugins for GUI.
        \end{itemize}
    \item What's next?
        \begin{itemize}
            \item Cleanup all the scripts and codes to be integrated. Have them unit tested and prepared for integration in the coming sprint. 
            \item David suggested to perform a performance benchmarking to see whether the new changes has any significance to the original version. 
            \item David is expecting detail reports on the plugins architecture and present the ways investigated on GUI plugins. 
            \item Ken suggested that integration should be done as a full group instead of subgroups. This because he had experienced the issues with merging using \texttt{git}.
        \end{itemize}
\end{enumerate} 

\end{document}  