\documentclass{letter}

\begin{document}

{\large \textbf{\underline{Meeting Minutes Taken on 26$^{th}$ August, 2008 at 1300 hours}}}

\textbf{Attendees:} Huang Jian, Cui, Fil, Ken, Ida, Keane, David \& Li Jiang 

\textbf{Excused:} Mohammad

\textbf{Next Meeting:} 02/09/2008 (Tuesday) @ 1300 hours 

\textbf{Contents:}

\begin{enumerate}
\item Progress Updates
	\begin{itemize}
		\item Plugin loaded from database.
			\begin{itemize}
				\item Generic hook is currently in place for file monitor.
			\end{itemize}
		\item Passdowns on plugin designs and concepts from group 3 to PFG was successful
			\begin{itemize}
					\item Several documents were released to PFG for development reference.
					\item General feedback on the documents were good.
			\end{itemize}
		\item Huang and Keane had started working on the GUI plugin
			\begin{itemize}
				\item Ticket 66 is aimed to be converted into a plugin. 
			\end{itemize}
	\end{itemize}
\item Next steps
	\begin{itemize}
		\item Daemon ``face-lift'' is in progress
			\begin{itemize}
				\item Fil: File monitor had been re-written.
			\end{itemize}
		\item API methods decomposition is in progress. API and plugin standard programming conventions have been set. 
			\begin{itemize}
				\item Cui, Keana, Ida and Huang are working on this. 
				\item David wants more plugins as examples to convince the customer.
			\end{itemize}
		\item An extra plugin is currently in the plan for next week presentation.
	\end{itemize}
\item Opens
	\begin{itemize}
		\item David: Document all the issue faced during development. 
		\item Li: Seconded David's comment on documenting the investigation process.
		 \item David stressed a lot on documentation.
		 \item David suggested present the incremental progress development to the customer will be good. 
		 \item David: What about Rails plugins?
		 	\begin{itemize}
				\item It was discussed and agreed that if plugins are developed based on Rails plugins, there will be a deployment problem on a server-farm like architecture. 
			\end{itemize}
	\end{itemize}
\end{enumerate} 
\end{document}  