\documentclass{article}
\usepackage{a4wide}

\begin{document}
\markright{Xiaodong Cui (1149546)}
\pagestyle{headings}

\begin{center}
{\LARGE\textbf{\underline{{Individual Milestone 5 Report}}}}
\end{center}

\section*{Executive Summary}

This is the first milestone since we have regrouped. In this new group, I have been working with other MSE students on plugins. I took about one week to understand the existing concepts about plugin, and discussed with others to understand what needed to be done. I also decomposed the filemonitor into some API files based on the API concepts, after all this, I spent some time to look at the GUI plugins as well.

\section*{Tasks and Activities Assigned}

\begin{itemize}
	\item Decompose filemonitor into seperated API files
	     \begin{itemize}
	        \item Sub-task 1: Looked at the API plugin concepts proposed by other MSE students and the file monitor system.
	           \begin{itemize}
					\item Description: Since I was new to the plugin stuff, it took me some time to look at those stuff, try to understand the whole concept, and had some research on different plugin implementation methods. Also I spent some time to look at the file monitor system in order to find out what can be decomposed to form APIs.
					\item Estimated time taken (planned): 25 hours
					\item Estimated time taken (actual):  20 hours (19/08/08-24/08/08)
				\end{itemize}
			\item Sub-task 2: Decomposed filemonitor into some APIs.
			   \begin{itemize}
					\item Description: We had agreed on the standards of writing API files, and decided that all those API files must be stored under earth\_api folder. I decomposed filemonitor into several API files,(Eapi\_Eta\_printer, Eapi\_file\_monitor, Eapi\_FileMonitor\_benchmark, Eapi\_logger) and reconstructed filemonitor to use methods defined within those API files.
					\item Affected files: 
					\begin{itemize}
					\item  \texttt{file\_monitor.rb}
					\item  \texttt{Eapi\_Eta\_printer}
					\item  \texttt{Eapi\_file\_monitor}
					\item  \texttt{Eapi\_FileMonitor\_benchmark}
					\item  \texttt{Eapi\_logger}
					\end{itemize}
					\item Estimated time taken (planned): 30 hours
					\item Estimated time taken (actual): 22 hours
					(25/08/08-28/08/08)
				\end{itemize}
			\item Sub-task 3: Load filemonitor as a plugin.
			        \begin{itemize}
					\item Description: followed some steps to load filemonitor as a plugin.
					\item Estimated time taken (planned): 5 hours
					\item Estimated time taken (actual): 3 hours (28/08/08-29/08/08)
				\end{itemize}	
	     \end{itemize}
	\item GUI plugin
	     \begin{itemize}
	         \item Sub-task 1: Rails plugin could be applied as GUI plugin for earth.
	            \begin{itemize}
	              \item Description: I had some research on rails plugin, and I think this can be used to write our GUI plugin.
					\item Estimated time taken (planned): 15 hours
					\item Estimated time taken (actual): 12 hours (29/08/08-31/08/08)
				 \end{itemize}
	         \item Sub-task 2: Constructed a simple GUI plugin adding a tab into earth, and display some information under the added tab.
	            \begin{itemize}
				    \item Description: I created a simple rails plugin (user\_usage), included two files one is called user\_usage.rb to include a new method (acts\_as\_add\_tab) to allow uses to create a tab, other one is called usage\_helper used to display information under user\_usage tab.
					\item Affected files: user\_usage plugin folder
					\item Estimated time taken (planned): 6 hour
					\item Estimated time taken (actual): 8 hours (31/08/08-02/09/08)
				 \end{itemize}
	     \end{itemize}
\end{itemize}

\section*{Resource Contributions}

For this milestone, I have estimated that I had spend about 71 hours (including 6 hours meeting time) over the spread of 3 weeks. The first week I was almost spent all the time on reading, because I just moved to this plugin group, I needed to understand what they had done for plugins up to milestone 4. The following two weeks I spent the time on decomposing and GUI plugin stuff.

\section*{Rooms for Improvement}

\begin{itemize}
   \item I think we need better communication between group members. 4 MSE students were assigned the decomposition part, but we seemed to work on that individually. Some API files created by one person might be created by another one as well. In addition, I worked with GUI plugin, and I believe another MSE student was working on that also, so the resources were split. I think we need to focus on one thing, and use our available resources to make it workable. 
\end{itemize}

\end{document}  