\documentclass{article}
\usepackage{a4wide}
\usepackage{hyperref}

\begin{document}
\markright{SEGP2 Plugin Group (8$^{th}$ September, 2008)}
\pagestyle{headings}

\begin{center}
{\textbf{\underline{SEGP2 Plugin Group Milestone 5 Report}}}
\end{center}

\noindent{\textbf{Total Hours Spend:} approx. ??? hours}

\section*{Executive Summary}

Milestone 5 began by forming an all Masters of Software Engineering students group to focus on developing a functional and usable plugin system for Earth. 

The group started with the plan of decomposing the entire development process into three major tasks:

\begin{enumerate}
	\item Decomposing the File Montior into API methods.
	\item Retrofit \texttt{earthd} to load plugins from the database.
	\item Streamlining the plugins deployment.
\end{enumerate}

Due to time constraints, and the forming of the new group, the group agreed to only complete the first two tasks for this sprint. 

At the end of the sprint, \texttt{earthd} was retrofitted with the new plugins loading mechanism. Also, the plugin architecture also sport an extension sub-architecture that allows plugins to have plugins as well. All these were integrated in a functional prototype that was demonstrated during the end of milestone presentation. 

Besides \texttt{earthd}, a few of the members also took the opportunity to explore how the Models, Views Controllers and Helpers can be made pluggable. It was suggested that the entire front-end needs to be revamped to support a toolkit like API architecture. However, this suggestion was dismissed as it is too complicated and there is not enough resources to complete such a feat. The results of the investigations were mixed, and it was agreed that a path will be finalized in the next sprint which the group will work on. 

The group achieved synergy by practicing pair, or rather peer, programming. Since Ken has less hours than the rest, the group had gave the administration role to him to run the group, while giving the development responsibilities were assumed by the rest. Besides administrations, Ken was also the main consult for doubts in the plugin system development, as he had been leading this development since Sprint 3. 

Overall, the group was able to deliver a solid plugin system for the back-end, and options to be considered for the MVC front-end. Our goal for the next sprint is to finish up the unfinished matters from this sprint and have the daemon plugins system online before the final integration of the entire system. 

\section*{Individual Reports}

Attached are the individual reports of each member of the group. 

\include{a1159155.1}

\include{a1149546.1}

\include{a1154924.1}

\include{a1154356.1}

\include{a1144332.1}

\include{a1155566.1}

%\include{Huang.1}

\end{document}  