\documentclass{article}
\usepackage{a4wide}
\usepackage{graphicx}
\pagestyle{headings}

\begin{document}
\title{\textbf{Milestone 5 Plan for Group 2}}\author{Ming Jie Tan}

\maketitle
\thispagestyle{empty}
\newpage{}

\thispagestyle{empty}
\tableofcontents
\newpage{}

\setcounter{page}{1}
\section{Introduction}

At the start of this milestone, the groups undertaking tasks altered. As a result, group 2 now consists of BESE students. As a result, most of the activities to be undertaken are continuations from the previous iteration. In addition to these tasks, as the other group is now attempting to further complete the plugin system, our group will also be providing feedback on the direction that the plugin system should be taking. Finally, group 2 will be aiming to update the repositories with all the code of completed tasks. 
The main aim for this iteration is to continue work on existing tickets while ensuring that completed tasks are integrated and tested properly.

\newpage{}
\section{Tasks}

The tasks to be undertaken are:
\begin{itemize}
	\item Acquiring Image Data
	\item Patenation of pages
	\item Feedback on Plugin System
	\item Testing and Integration
\end{itemize}

\subsection{Acquisition of Image Data}

Ticket 29 requires us to be able to access image data. In terms of completing this task this iteration, using the investigation from the last milestone, the task requires further investigation into the possibly combined use of the rsp naming convention, in addition to the possible use of some existing open source code that parses image files without opening them. However as these existing solutions are only in alpha, they do not cover all necessary file formats. This solution may not be possible at present as it may after testing result in slowing the system significantly.

\subsection{Patenation of pages}

Currently this is a bug where sorting is unable to work on folders where there aren't more than one page of results. This will require some look into the existing haml files in order to determine what each section of code is doing in order to locate and fix the problem.

\subsection{Feedback on Plugin System}

With the Plugin System being redone, as the design choices are made for the system, group 2 will provide feedback on what should or shouldn't be added to the system in order to get the functionality of the system up and running. This process will be an on going one, with communication with group 1.

\subsection{Testing and Integration}

This task involves the merging of all the existing working code and ensuring that it is working. This will require testing at the root level once all the code has been gathered.

\section{Conclusion}

Overall this iteration is mostly one of completing existing tasks while polishing up completed tasks rather than undertaking any new tasks.

\end{document}
