\documentclass{letter}

\begin{document}

{\large \textbf{\underline{SEGP2 Milestone 2 Group Report of Subgroup 3}}}

\textbf{Total Hours Spend:} approx. 137 hours

Milestone 2 started with the assignment of tickets from the group meeting. The following are the tickets and tasks assigned:

\begin{itemize}
   \item Ticket 23: To allow tagging of files and directories in Earth.
   \item Ticket 27: To allow the MIME-type or the magic numbers of files to be stored as useful metadata.
   \item Database Study: To study and document the database setup for Earth.
   \item Test on Ticket 66.
\end{itemize}

The following are the owners and the progress made by the tasks owners:

\begin{itemize}
   \item Ticket 23:
      \begin{itemize}
         \item Owner: Jonathan Velasco
         \item Progress: He had completed the task by implementing a simple M:M relationship table in the database. Also, he had demoed a prototype of the implementation. The current plan is to get the idea tested and then move on to make it as a plugin once the plugin system or architecture is ready for production use. 
      \end{itemize}
   \item Ticket 27:
      \begin{itemize}
         \item Owner: Sahil Choujar
         \item Progress: Due to an unexpected catastrophic hardware failure, this ticket has no progress to-date. 
      \end{itemize}
   \item Database Study
      \begin{itemize}
         \item Owner: Jian Huang
         \item Progress: He had completed the initial study of the database setup for Earth. A public draft of the database usage had been released as of the end of Milestone 2. 
      \end{itemize}
   \item Test on Ticket 66
      \begin{itemize}
         \item Owner: Ken S'ng Wong
         \item Progress: The ticket was not assigned in the Master Plan, but the group agreed to have the solution implmented in Milestone 1 to be tested in this milestone. The ticket was tested and refined as of the end of this milestone. 
      \end{itemize}
\end{itemize}



\end{document}  
