\documentclass{letter}

\begin{document}

{\large \textbf{\underline{Meeting Minutes Taken on 12$^{th}$ May, 2008 at 1415 hours}}}\\

\textbf{Attendees:} Callum, Alex, George, Ming, Filimoni, Ken, Cui, Hemant, Mohammed, Hill, Keane, Ida 

\textbf{Late:} George, Sahil

\textbf{Excused:} None

\textbf{Absent:} Hemant

\textbf{Next Meeting:} 12/05/2008 (Monday) @ 1415 hours

\textbf{Contents:}

\begin{enumerate}
\item Minutes on 5$^{th}$ May, 2008 Reviewed
	\begin{itemize}
	\item Github Leaders
	\item Subgroup Tasks established
	\item Subgroup meeting times with lecturers organised
	\end{itemize}
\item Milestone 2 Progress 
	\begin{itemize}
	\item Ticket 138 (filtered query optimisation) - options being researched, may need database optimization and use of postgres optimizer, but still looking at queries.
	\item Ticket 27 is restored to being unfinished due to unforeseen circumstances
	\item Ticket 146 (running test continuously) - operational, but can't run at the same time as normal daemon currently.
	\item Ticket 42 - addition of metadata into the databases will be implemented to allow search to be able to look for details about job name, shot name and sequence name. 
	\item Ticket 23 - rough sketch laid out for how to implement tagging.
	\item Documentation - Plugin and Database documentation is currently being undertaken.
	\item Milestone 1 Integration - requires Git push as well as test cases and testing.
	\item Group main contacts to maintain documentation - Ken (G3), Ming(G2), Fil(G1)
	\end{itemize}
\item Git Repository
	\begin{itemize}
	\item All group repositories are online and every has been invited.
	\item Trac access is available to members and should be used to comment on the various tasks.
	\item Documentation and implementation of Trac processes and addition of ticket statuses to be undertaken by Callum.
	\end{itemize}
\end{enumerate} 
\end{document}  