\documentclass{article}
\begin{document}
\markright{JONATHAN VELASCO (1135461)}
\pagestyle{headings}

\begin{center}
{\LARGE\textbf{\underline{{Individual Milestone 7 Report}}}}
\end{center}

\section*{Executive Summary}

I collaborated doing the integration of the different repositories into a final version to give to RSP. 

\section*{Tasks and Activities Performed}

\begin{itemize}
	\item Integration of repositories from group 1 and 2
	     \begin{itemize}
                \item Description: With the help of Mohammad, I created a clean fork of Earth from Mathew.  This new repository is Jonv/Earth.  Several branches were created in order to merge group 1 and 2, leaving the master branch as the version that Mathew have.
                \item Idea/Solution: N/A
                \item Affected files: The files that had merge conflicts were:
                                      \begin{itemize}
                                       \item earth/app/controllers/application.rb
                                       \item earth/app/controllers/browser\_controller.rb
                                       \item earth/app/controllers/graph\_controller.rb
                                       \item earth/app/helpers/application\_helper.rb
                                       \item earth/app/helpers/usages\_helper.rb
                                       \item earth/config/usage\_routes.rb
                                       \item earth/lib/earth\_api\_utilities.rb
                                       \item earth/lib/earth\_plugin\_interface plugin\_manager.rb
                                       \item earth/lib/earth\_plugins file\_monitor.rb
                                       \item earth/script/earthd
                                       \item earth/script/sign\_plugin
                                      \end{itemize}
                \item Git commits: 812fbd92078a4024bad5a40c09673773eba96b09
                \item Estimated time taken (planned): 5 hours
                \item Estimated time taken (actual): 7 hours 
            
	     \end{itemize}
	\item Integration of Cui work into final repository for RSP
	     \begin{itemize}
	        \item Description: Upon request from Cui, I created a new branch into Jonv/Earth in order to integrate ticket 131 into the final version of Earth.  Those files with merge conflict were indicated to Cui so that he could fix them.
		\item Idea/Solution: N/A
		\item Affected files: The files that had merge conflicts were:
                                      \begin{itemize}
                                       \item app/controllers/browser\_controller.rb  
                                       \item app/views/browser/show.html.haml
                                      \end{itemize}
		\item Git commits:  2c124c52b8b14bbf5072648286f0fe9a4d3fe7ca
                \item Estimated time taken (planned): N/A              
		\item Estimated time taken (actual): 3
	      \end{itemize}
       
                
	\item Elaboration of documents
	     \begin{itemize}
	         \item Description: Elaboration of report (milestone 6)
	         \item Idea/Solution: N/A
	         \item Affected files: \texttt{Documents/Reports/Milestone6/tickets\_group/a1135461.tex}
	         \item Git commits:   7d19a0b3ba7b58e63edf605c369ceceb7c7c661c
		 \item Estimated time taken (planned): N/A
	         \item Estimated time taken (actual): 0.5 hours 
	     \end{itemize}
\end{itemize}

\section*{Resource Contributions}

The integration this  time went easier due to the experience doing integration during mileston 6.  Several decision meettings were held with the group leaders from the groups 1, 2 and 3 in order to decide the best way to do the integration.  The total time taken on this spring was 13.5 hours, from which, 0.5 hour was documents elaboration, 3 hours on meetings and 10 hours doing integration. 





\end{document}  